---
title: "models"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1. Fitting the final model using mlogit library

```{r}
library(mlogit)
HH_dt_2_out$numcars <- as.numeric(as.character(HH_dt_2_out$numcars))
HH_dt_2_out$numcars <- factor(HH_dt_2_out$numcars)

# transform data to long format as needed by mlogit
mnlogit_dt_out <- mlogit.data(HH_dt_2_out, choice = "numcars", shape = "wide") 


#fit null model (only intercept)
fm_null <- formula(numcars ~ 1 | 1 | 1)
fit_null <- mnlogit(fm_null, mnlogit_dt_out, ncores=4, choiceVar = "alt")

# fit preliminary model as a comparison model 
fm1 <- formula(numcars ~ 1 | numlic + region2 + income_numerical + 
    quali_nv + CSyes + workers + CSmultiple + nummots + housing_type + 
    triplength_avg + quali_opnv + oldHH + parttime + tripsavg + 
    hh_children + numped + metro28 + train28 + garage + bus28 | 1)
fit1 <- mnlogit(fm1, mnlogit_dt_out, ncores=4, choiceVar = "alt")

# fit final model formulation including nonlinear terms
fm_new <- formula(numcars ~  1| numlic + region2 + income_numerical + I(numlic^2) + 
    quali_nv + I(income_numerical^2) + CSyes + workers + CSmultiple + 
    log(nummots1) + triplength_avg + housing_type + quali_opnv + 
    I(triplength_avg^2) + oldHH + parttime + hh_children + numped + 
    tripsavg + metro28 + train28 + garage + bus28 + I(parttime^2)|1)
fit_new <- mnlogit(fm_new, mnlogit_dt_out, ncores=4, choiceVar = "alt")

```

2. Model validation

2.1 Overall model evaluations and pseudo R2
```{r}

# z-statistics and z-tests of individual predictors:
summary(fit_new)

#Tests against the null-model

# Wald test

waldtest(fit_new, fit_null)

# Score test (using mlogit)
model1 <- mlogit(numcars ~  1| numlic + region2 + income_numerical + I(numlic^2) + 
    quali_nv + I(income_numerical^2) + CSyes + workers + CSmultiple + 
    log(nummots1) + triplength_avg + housing_type + quali_opnv + 
    I(triplength_avg^2) + oldHH + parttime + hh_children + numped + 
    tripsavg + metro28 + train28 + garage + bus28 + I(parttime^2), data = mnlogit_dt_out)
model2 <- mlogit(numcars ~ 1|numlic, data = mnlogit_dt_out)
mlogit::scoretest(model2, model1)

# Likelihood ratio test

lrtest(fit_null, fit_new)

# AIC:
AIC(fit_new)
AIC(fit_null)

# compare preliminary model and model featuring non-linear terms -> nonlinearity performs better

lrtest(fit_new, fit1)

AIC(fit_new)
AIC(fit1)

# compute Pseudo R2 measures

#Source: http://dwoll.de/rexrepos/posts/regressionMultinom.html#mcfadden-cox-snell-and-nagelkerke-pseudo-r2

LL0 <- logLik(fit_null)
LL1 <- logLik(fit_new)
N <- nrow(HH_dt_2_out)

#mc fadden pseudo r2 
mcfadden <- as.vector(1 - ((LL1) / (LL0)))

# cox and snell r2 
cox <- as.vector(1 - exp((2/N) * (LL0 - LL1)))

# nagelkerke r2
nagelkerke <- as.vector((1 - exp((2/N) * (LL0 - LL1))) / (1 - exp((2/N)*LL0)))

```

2.2 Hosmer-Lemeshow standardization for large samples
```{r}
#n = 70320
#event number = 4
#target sample size= 500
#k=1000

#Sample a dataset with 500 rows from the big dataset that has the same distribution of outcomes as the real dataset
#do model on it
# do test on it 
# save HL statistic
# find distribution of HL statistic

dplyr::count(HH_dt_2_out,numcars)
#0	7467 -> 10.6%	-> 53		
#1	35909	-> 51% -> 255		
#2	21762	-> 31%	-> 155	
#3	5182 -> 7.4% -> 37

HL_dist <- as.matrix(data.frame(t(c("1"))))
colnames(HL_dist) <- c("Stat")

#!long runtime!
for (i in 1:1000){
 a<- sample(subset(HH_dt_2_out, numcars == "0"), 53)
 b<- sample(subset(HH_dt_2_out, numcars == "1"), 255)
 c <- sample(subset(HH_dt_2_out, numcars == "2"), 155)
 d<- sample(subset(HH_dt_2_out, numcars == "3"), 37)
 df_test <- rbind(a,b,c,d)
 
fit_HLsim <- multinom(numcars ~ numlic + region2 + income_numerical + I(numlic^2) + 
    quali_nv + I(income_numerical^2) + CSyes + workers + CSmultiple + 
    log(nummots1) + triplength_avg + housing_type + quali_opnv + 
    I(triplength_avg^2) + oldHH + parttime + hh_children + numped + 
    tripsavg + metro28 + train28 + garage + bus28 + I(parttime^2), data = df_test)
 
HLtest <- logitgof(df_test$numcars, fitted(fit_HLsim))
HLstat <- HLtest$statistic

HL_dist <- rbind(HL_dist, HLstat)

}

HL_dist <- as.data.frame(HL_dist)
HL_dist$Stat <- as.numeric(as.character(HL_dist$Stat))
hist(HL_dist$Stat)

#Xiquadrat verteilung für Xi(10-2) für 95% quantil:  2.73

prob = 1 - ecdf(HL_dist$Stat)(2.73)
prob
runif(1)

```

3. Results of the MNL model for the analysis of general influence factors on car ownership levels in Germany

3.1 Coefficient table / Log-odds
```{r}
options(scipen = 999)

summary <- summary(fit_new)
coeffs <- summary$CoefTable
coeffs <- as.data.frame(coeffs)
coeffs <- rownames_to_column(coeffs)
coeffs$`t-value` <- NULL

coeffs1 <- coeffs[seq(1, 114, by=3),]
coeffs2 <- coeffs[seq(2, 114, by=3),]
coeffs3 <- coeffs[seq(3, 114, by=3),]

coeffs_total <- data.frame(coeffs1, coeffs2, coeffs3)
coeffs_total$rowname.1 <- NULL
coeffs_total$rowname.2 <- NULL

coeffs_total$rowname<-  sub(":1", "", coeffs_total$rowname)
coeffs_total$rowname[coeffs_total$rowname=="I(numlic^2)"] <- "licenses squared"
coeffs_total$rowname[coeffs_total$rowname=="I(parttime^2)"] <- "parttime squared"
coeffs_total$rowname[coeffs_total$rowname=="I(income_numerical^2)"] <- "income squared"
coeffs_total$rowname[coeffs_total$rowname=="I(triplength_avg^2)"] <- "av.triplength squared"
coeffs_total$rowname[coeffs_total$rowname=="log(nummots1)"] <- "motorbikes (log)"

coeffs_total$rowname[coeffs_total$rowname=="numlic"] <- "licenses"
coeffs_total$rowname[coeffs_total$rowname=="income_numerical"] <- "income"
coeffs_total$rowname[coeffs_total$rowname=="triplength_avg"] <- "av.triplength"
coeffs_total$rowname[coeffs_total$rowname=="workers"] <- "fulltime"
coeffs_total$rowname[coeffs_total$rowname=="numped"] <- "bikes"
coeffs_total$rowname[coeffs_total$rowname=="tripsavg"] <- "av.trips"
coeffs_total$rowname[coeffs_total$rowname=="CSyes1"] <- "carsharing"
coeffs_total$rowname[coeffs_total$rowname=="CSmultiple1"] <- "m.carsharing"
coeffs_total$rowname[coeffs_total$rowname=="nummots"] <- "motorbikes"
coeffs_total$rowname[coeffs_total$rowname=="parttime"] <- "parttime"
coeffs_total$rowname[coeffs_total$rowname=="region2suburban"] <- "suburban"
coeffs_total$rowname[coeffs_total$rowname=="region2rural"] <- "rural"
coeffs_total$rowname[coeffs_total$rowname=="oldHH1"] <- "old"
coeffs_total$rowname[coeffs_total$rowname=="hh_children1"] <- "children"
coeffs_total$rowname[coeffs_total$rowname=="housing_typemultifamily_h"] <- "multifamily"
coeffs_total$rowname[coeffs_total$rowname=="housing_typeapartmentbuilding"] <- "apartmentbuilding"
coeffs_total$rowname[coeffs_total$rowname=="housing_typeother"] <- "other"
coeffs_total$rowname[coeffs_total$rowname=="garage1"] <- "garage"

coeffs_total$rowname[coeffs_total$rowname=="quali_nv2"] <- "ps.2"
coeffs_total$rowname[coeffs_total$rowname=="quali_nv3"] <- "ps.3"
coeffs_total$rowname[coeffs_total$rowname=="quali_nv4"] <- "ps.4"


coeffs_total$rowname[coeffs_total$rowname=="quali_opnv2"] <- "pt.2"
coeffs_total$rowname[coeffs_total$rowname=="quali_opnv3"] <- "pt.3"
coeffs_total$rowname[coeffs_total$rowname=="quali_opnv4"] <- "pt.4"


coeffs_total$rowname[coeffs_total$rowname=="bus28_middle"] <- "bus.2"
coeffs_total$rowname[coeffs_total$rowname=="bus28_far"] <- "bus.3"
coeffs_total$rowname[coeffs_total$rowname=="bus28_rfar"] <- "bus.4"


coeffs_total$rowname[coeffs_total$rowname=="train28_middle"] <- "train.2"
coeffs_total$rowname[coeffs_total$rowname=="train28_far"] <- "train.3"
coeffs_total$rowname[coeffs_total$rowname=="train28_rfar"] <- "train.4"

coeffs_total$rowname[coeffs_total$rowname=="metro28_middle"] <- "metro.2"
coeffs_total$rowname[coeffs_total$rowname=="metro28_far"] <- "metro.3"
coeffs_total$rowname[coeffs_total$rowname=="metro28_rfar"] <- "metro.4"

colnames(coeffs_total)<- c("Variable","Parameter","Std. Error", "Sig1.", "Parameter","Std. Error", "Sig2.", "Parameter","Std. Error", "Sig3.")

for(i in 1:38) {
  if (coeffs_total$Sig1.[i] < 0.01) {
    coeffs_total$Sig1.[i] <- "***"
  }
  else if (coeffs_total$Sig1.[i] < 0.05) {
    coeffs_total$Sig1.[i] <- "**"
  }
  else if (coeffs_total$Sig1.[i] < 0.1) {
    coeffs_total$Sig1.[i] <- "*"
  }
  
  else{
    coeffs_total$Sig1.[i] <- ""
  }
}

for(i in 1:38) {
  if (coeffs_total$Sig2.[i] < 0.01) {
    coeffs_total$Sig2.[i] <- "***"
  }
  else if (coeffs_total$Sig2.[i] < 0.05) {
    coeffs_total$Sig2.[i] <- "**"
  }
   else if (coeffs_total$Sig2.[i] < 0.1) {
    coeffs_total$Sig2.[i] <- "*"
   }
  else{
    coeffs_total$Sig2.[i] <- ""
  }
}


for(i in 1:38) {
  if (coeffs_total$Sig3.[i] < 0.01) {
    coeffs_total$Sig3.[i] <- "***"
  }
  else if (coeffs_total$Sig3.[i] < 0.05) {
    coeffs_total$Sig3.[i] <- "**"
  }
   else if (coeffs_total$Sig3.[i] < 0.1) {
    coeffs_total$Sig3.[i] <- "*"
   }
  else{
    coeffs_total$Sig3.[i] <- ""
  }
 }


print(xtable(coeffs_total, type = "latex",digits=c(0,0,3,3,0,3,3,0,3,3,0)),include.rownames=FALSE, file = "coeffs_model.tex")
```

3.2 Odds ratios - Table
```{r}
#relative risk rates / the odds ratio 

# for relative risk ratio (odds) instead of log odds which is the output of the model

coeffs_odds <- coeffs_total
coeffs_odds <- coeffs_odds[-c(3,4,6,7,9,10)]
coeffs_odds$Parameter <- exp(coeffs_odds$Parameter)
coeffs_odds$Parameter.1 <- exp(coeffs_odds$Parameter.1)
coeffs_odds$Parameter.2 <- exp(coeffs_odds$Parameter.2)

print(xtable(coeffs_odds, type = "latex",digits=c(0,0,3,3,3)),include.rownames=FALSE, file = "coeffs_odds.tex")
```

4. Fit the model again using the package multinom for further effect calculations
```{r}
fit_multinom <- multinom(numcars ~numlic + region2 + income_numerical + I(numlic^2) + 
    quali_nv + I(income_numerical^2) + CSyes + workers + CSmultiple + 
    log(nummots1) + triplength_avg + housing_type + quali_opnv + 
    I(triplength_avg^2) + oldHH + parttime + hh_children + numped + 
    tripsavg + metro28 + train28 + garage + bus28 + I(parttime^2), data = HH_dt_2_out,maxit=250)

fm_new <- formula(numcars ~  1| numlic + region2 + income_numerical + I(numlic^2) + 
    quali_nv + I(income_numerical^2) + CSyes + workers + CSmultiple + 
    log(nummots1) + triplength_avg + housing_type + quali_opnv + 
    I(triplength_avg^2) + oldHH + parttime + hh_children + numped + 
    tripsavg + metro28 + train28 + garage + bus28 + I(parttime^2)|1)
fit_new <- mnlogit(fm_new, mnlogit_dt_out, ncores=4, choiceVar = "alt")

fit_multinom_v3 <- fit_multinom
cf2 <- matrix(fit_multinom_v3$wts, nrow=39)  
fit_new.cf <- coef(fit_new)
cf2[2:nrow(cf2), 2:ncol(cf2)] <- (matrix(fit_new.cf,nrow=3))

fit_multinom_v3$wts <- c(cf2)
fit_multinom_v3$fitted.values <- fit_new$probabilities

```


5.1 Computation of average marginal effects (long computation time)

```{r}

# AMEs are calculated differently depending on the number of corresponding coefficients, first AMEs are calculated for variables with one level, than for variables with four levels and lastly for variables with three levels (e.g. region). Lastly, the AMEs for the number of motorbikes is computed separately, due to its logit transformation

AME_df <- as.matrix(data.frame(t(c("name", "zero_cars","1_car","2_cars","3_cars"))))
colnames(AME_df) <- c("name", "zero_cars","one_car","two_cars","three_cars")

a.names <- names(fit_new$model)[- c(1, 22:25)]

names_num <- a.names[-c(2,4,8,10:11,17:18,20)]
names_cat <- a.names[c(4,10:11,17:18,20)]

  for(i in names_num){
  
  a <- marginal_effects(data=HH_dt_2_out, fit_multinom_v3, variables = i,category="0")
  a_mean <- mean(a[,1])
  b <- marginal_effects(data=HH_dt_2_out, multinom_int3, variables = i,category="1")
  b_mean <- mean(b[,1])
  c <- marginal_effects(data=HH_dt_2_out, fit_multinom_v3, variables = i,category="2")
  c_mean <- mean(c[,1])
  d <- marginal_effects(data=HH_dt_2_out, fit_multinom_v3, variables =i,category="3")
  d_mean <- mean(d[,1])
  v <- c(i,a_mean,b_mean,c_mean,d_mean)
  AME_df <- insertRow(AME_df,1,v)
}

  for(i in names_cat){
  
  a <- marginal_effects(data=HH_dt_2_out, fit_multinom_v3, variables = i,category="0")
  a_mean <- mean(a[,1])
  a_mean2 <- mean(a[,2])
  a_mean3 <- mean(a[,3])
  b <- marginal_effects(data=HH_dt_2_out, fit_multinom_v3, variables = i,category="1")
  b_mean <- mean(b[,1])
  b_mean2 <- mean(b[,2])
  b_mean3 <- mean(b[,3])
  c <- marginal_effects(data=HH_dt_2_out, fit_multinom_v3, variables = i,category="2")
  c_mean <- mean(c[,1])
  c_mean2 <- mean(c[,2])
  c_mean3 <- mean(c[,3])
  d <- marginal_effects(data=HH_dt_2_out, fit_multinom_v3, variables =i,category="3")
  d_mean <- mean(d[,1])
  d_mean2 <- mean(d[,2])
  d_mean3 <- mean(d[,3])

  v <- c(paste0(i,"2"),a_mean,b_mean,c_mean,d_mean)
  v2 <- c(paste0(i,"3"),a_mean2,b_mean2,c_mean2,d_mean2)
  v3 <- c(paste0(i,"4"),a_mean3,b_mean3,c_mean3,d_mean3)
  AME_df <- insertRow(AME_df,1,v)
  AME_df <- insertRow(AME_df,1,v2)
  AME_df <- insertRow(AME_df,1,v3)
  }

# Calculation of AMEs for the region Variable

 a <- marginal_effects(data=HH_dt_2_out, fit_multinom_v3, variables = "region2",category="0")
  a_mean <- mean(a[,1])
  a_mean2 <- mean(a[,2])
  b <- marginal_effects(data=HH_dt_2_out, fit_multinom_v3, variables = "region2",category="1")
  b_mean <- mean(b[,1])
  b_mean2 <- mean(b[,2])
  c <- marginal_effects(data=HH_dt_2_out, fit_multinom_v3, variables = "region2",category="2")
  c_mean <- mean(c[,1])
  c_mean2 <- mean(c[,2])
  d <- marginal_effects(data=HH_dt_2_out, fit_multinom_v3, variables = "region2",category="3")
  d_mean <- mean(d[,1])
  d_mean2 <- mean(d[,2])

  v <- c(paste0("region2","suburban"),a_mean,b_mean,c_mean,d_mean)
  v2 <- c(paste0("region2","rural"),a_mean2,b_mean2,c_mean2,d_mean2)
  
  AME_df <- insertRow(AME_df,1,v)
  AME_df <- insertRow(AME_df,1,v2)
  
# Manual calculations of the AME for the number of motorbikes, due to the log transformation

B <- coef(fit_new)
b <- c(0,B[c("log(nummots1):1", "log(nummots1):2", "log(nummots1):3")])
pb <- probs[,2] * b[2]  + probs[,3] * b[3] + probs[,4] * b[4]
me <- matrix(0, nrow(probs), ncol(probs))
for(j in 1:4) {
  me[,j] <- probs[,j] * (b[j] - pb)
 }
r<- apply(me, 2, mean)
v <- c("log(nummots1)", r)
AME_df <- insertRow(AME_df,1,v)


# clean dataframe
AME_df <- AME_df[-c(34),]
AME_df <- as.data.frame(AME_df)
AME_df$zero_cars <- as.numeric(as.character((AME_df$zero_cars)))
AME_df$zero_cars <- round(AME_df$zero_cars,3)

AME_df$one_car <- as.numeric(as.character((AME_df$one_car)))
AME_df$one_car <- round(AME_df$one_car,3)

AME_df$two_cars <- as.numeric(as.character((AME_df$two_cars)))
AME_df$two_cars <- round(AME_df$two_cars,3)

AME_df$three_cars <- as.numeric(as.character((AME_df$three_cars)))
AME_df$three_cars <- round(AME_df$three_cars,3)

#make table of AMEs
AME_df$name <- as.character(AME_df$name)
AME_df$name[AME_df$name=="numlic"] <- "licenses"
AME_df$name[AME_df$name=="income_numerical"] <- "income"
AME_df$name[AME_df$name=="triplength_avg"] <- "av.triplength"
AME_df$name[AME_df$name=="workers"] <- "fulltime"
AME_df$name[AME_df$name=="numped"] <- "bikes"
AME_df$name[AME_df$name=="tripsavg"] <- "av.trips"
AME_df$name[AME_df$name=="CSyes"] <- "carsharing"
AME_df$name[AME_df$name=="CSmultiple"] <- "m.carsharing"
AME_df$name[AME_df$name=="log(nummots1)"] <- "motorbikes"
AME_df$name[AME_df$name=="parttime"] <- "parttime"
AME_df$name[AME_df$name=="region2suburban"] <- "suburban"
AME_df$name[AME_df$name=="region2rural"] <- "rural"
AME_df$name[AME_df$name=="oldHH"] <- "old"
AME_df$name[AME_df$name=="hh_children"] <- "children"
AME_df$name[AME_df$name=="housing_type2"] <- "multifamily"
AME_df$name[AME_df$name=="housing_type3"] <- "apartmentbuilding"
AME_df$name[AME_df$name=="housing_type4"] <- "other"
AME_df$name[AME_df$name=="garage"] <- "garage"

AME_df$name[AME_df$name=="quali_nv2"] <- "ps.2"
AME_df$name[AME_df$name=="quali_nv3"] <- "ps.3"
AME_df$name[AME_df$name=="quali_nv4"] <- "ps.4"


AME_df$name[AME_df$name=="quali_opnv2"] <- "pt.2"
AME_df$name[AME_df$name=="quali_opnv3"] <- "pt.3"
AME_df$name[AME_df$name=="quali_opnv4"] <- "pt.4"


AME_df$name[AME_df$name=="bus282"] <- "bus.2"
AME_df$name[AME_df$name=="bus283"] <- "bus.3"
AME_df$name[AME_df$name=="bus284"] <- "bus.4"


AME_df$name[AME_df$name=="train282"] <- "train.2"
AME_df$name[AME_df$name=="train283"] <- "train.3"
AME_df$name[AME_df$name=="train284"] <- "train.4"

AME_df$name[AME_df$name=="metro282"] <- "metro.2"
AME_df$name[AME_df$name=="metro283"] <- "metro.3"
AME_df$name[AME_df$name=="metro284"] <- "metro.4"

```

5.2 Computation of Standardized coefficients

```{r}
importance_ml <- as.data.frame(coef(fit_new))
importance_ml <- rownames_to_column(importance_ml)
importance_ml1 <- importance_ml[1:38,]
importance_ml2 <- importance_ml[39:76,]
importance_ml3 <- importance_ml[77:114,]
importance_ml_final <- data.frame(importance_ml1, importance_ml2, importance_ml3)
importance_ml_final$rowname.1 <- NULL
importance_ml_final$rowname.2 <- NULL
colnames(importance_ml_final)<- c("Variable","One car","Two cars", "Three and more cars")
importance_ml_final <- importance_ml_final[order(importance_ml_final$Variable),]
importance_ml_final <- filter(importance_ml_final, Variable!= c("(Intercept):1"))
importance_ml_final <- filter(importance_ml_final, Variable!= c("I(numlic^2):1"))
importance_ml_final <- filter(importance_ml_final, Variable!= c("I(income_numerical^2):1"))
importance_ml_final <- filter(importance_ml_final, Variable!= c("I(triplength_avg^2):1"))
importance_ml_final <- filter(importance_ml_final, Variable!= c("I(workers^2):1"))
importance_ml_final <- filter(importance_ml_final, Variable!= c("I(parttime^2):1"))

#standard deviation of variables
relevant_vars <- names(fit_new$model)[2:21]
SD_df <- HH_dt_2_out[,relevant_vars, with=FALSE] 
alloc.col(SD_df, 200)
test_dummies <- fastDummies::dummy_cols(SD_df, remove_first_dummy = TRUE, remove_selected_columns = TRUE)
test_dummies$nummots1 <- log(test_dummies$nummots1)
names(test_dummies)[names(test_dummies) == 'nummots1'] <- 'log(nummots1)'
variables_SD <- apply(test_dummies,2,sd)
variables_SD <- as.data.frame(variables_SD)
variables_SD <- rownames_to_column(variables_SD)
variables_SD <- variables_SD[order(variables_SD$rowname),]

# calculate standardized coefficients
importance_f <- importance_ml_final
result_importance <- data.frame(importance_f, variables_SD)
result_importance$standardized_coef_1 <- abs(result_importance$One.car * result_importance$variables_SD)
result_importance$standardized_coef_2 <- abs(result_importance$Two.cars * result_importance$variables_SD)
result_importance$standardized_coef_3 <- abs(result_importance$Three.and.more.cars * result_importance$variables_SD)
result_importance$standardized_coef_total <- result_importance$standardized_coef_1 + result_importance$standardized_coef_2 + result_importance$standardized_coef_3

result_importance <- result_importance[order(result_importance$standardized_coef_total, decreasing=TRUE),]

result_importance2<- data.frame(result_importance$rowname,result_importance$standardized_coef_total)
colnames(result_importance2)<- c("rowname","Standardizedcoef")
result_importance2$rank <- c(1:33)
result_importance2$relimp <- result_importance2$Standardizedcoef/sum(result_importance2$Standardizedcoef)

# change names
result_importance2$rowname <- as.character(result_importance2$rowname)
result_importance2$rowname<-  sub("_", "", result_importance2$rowname)
result_importance2$rowname<-  sub("_", "", result_importance2$rowname)

result_importance2$rowname[result_importance2$rowname=="log(nummots1)"] <- "motorbikes"
result_importance2$rowname[result_importance2$rowname=="numlic"] <- "licenses"
result_importance2$rowname[result_importance2$rowname=="incomenumerical"] <- "income"
result_importance2$rowname[result_importance2$rowname=="triplengthavg"] <- "av.triplength"
result_importance2$rowname[result_importance2$rowname=="workers"] <- "fulltime"
result_importance2$rowname[result_importance2$rowname=="numped"] <- "bikes"
result_importance2$rowname[result_importance2$rowname=="tripsavg"] <- "av.trips"
result_importance2$rowname[result_importance2$rowname=="CSyes1"] <- "carsharing"
result_importance2$rowname[result_importance2$rowname=="CSmultiple1"] <- "m.carsharing"
result_importance2$rowname[result_importance2$rowname=="parttime"] <- "parttime"
result_importance2$rowname[result_importance2$rowname=="region2suburban"] <- "suburban"
result_importance2$rowname[result_importance2$rowname=="region2rural"] <- "rural"
result_importance2$rowname[result_importance2$rowname=="oldHH1"] <- "old"
result_importance2$rowname[result_importance2$rowname=="hh_children1"] <- "children"
result_importance2$rowname[result_importance2$rowname=="housingtypemultifamily_h"] <- "multifamily"
result_importance2$rowname[result_importance2$rowname=="housingtypeapartmentbuilding"] <- "apartmentbuilding"
result_importance2$rowname[result_importance2$rowname=="housingtypeother"] <- "other"
result_importance2$rowname[result_importance2$rowname=="garage1"] <- "garage"

result_importance2$rowname[result_importance2$rowname=="qualinv2"] <- "ps.2"
result_importance2$rowname[result_importance2$rowname=="qualinv3"] <- "ps.3"
result_importance2$rowname[result_importance2$rowname=="qualinv4"] <- "ps.4"

result_importance2$rowname[result_importance2$rowname=="qualiopnv2"] <- "pt.2"
result_importance2$rowname[result_importance2$rowname=="qualiopnv3"] <- "pt.3"
result_importance2$rowname[result_importance2$rowname=="qualiopnv4"] <- "pt.4"

result_importance2$rowname[result_importance2$rowname=="bus28middle"] <- "bus.2"
result_importance2$rowname[result_importance2$rowname=="bus28far"] <- "bus.3"
result_importance2$rowname[result_importance2$rowname=="bus28rfar"] <- "bus.4"

result_importance2$rowname[result_importance2$rowname=="train28middle"] <- "train.2"
result_importance2$rowname[result_importance2$rowname=="train28far"] <- "train.3"
result_importance2$rowname[result_importance2$rowname=="train28rfar"] <- "train.4"

result_importance2$rowname[result_importance2$rowname=="metro28middle"] <- "metro.2"
result_importance2$rowname[result_importance2$rowname=="metro28far"] <- "metro.3"
result_importance2$rowname[result_importance2$rowname=="metro28rfar"] <- "metro.4"

```

3.5 Merge AMEs and standardized coefficients and make table

```{r}

table_AMEstand <- merge(AME_df, result_importance2, by.x = "name", by.y="rowname")
table_AMEstand<- table_AMEstand[order(table_AMEstand$rank, decreasing=FALSE),]

print(xtable(table_AMEstand, type = "latex",digits=c(0,0,3,3,3,3,1,0,2)),include.rownames=FALSE, file = "AME2stand.tex")

```
