---
title: "Plot"
output: html_document
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)

```

Function to save plots to pdf
```{r}
install.packages('ggpubr')
library(ggpubr)

savepdf <- function(file, width=16, height=6)
{
  fname <- paste(file,".pdf",sep="")
  pdf(fname, width=width/2.54, height=height/2.54,
      pointsize=10)
  par(mgp=c(2.2,0.45,0), tcl=-0.4, mar=c(3.3,3.6,1.1,1.1))
}

savepdf4 <- function(file, width=16.5, height=7)
{
  fname <- paste(file,".pdf",sep="")
  pdf(fname, width=width/2.54, height=height/2.54,
      pointsize=10)
  par(mgp=c(2.2,0.45,0), tcl=-0.4, mar=c(3.3,3.6,1.1,1.1))
}


savepdf5 <- function(file, width=18, height=6)
{
  fname <- paste(file,".pdf",sep="")
  pdf(fname, width=width/2.54, height=height/2.54,
      pointsize=10)
  par(mgp=c(2.2,0.45,0), tcl=-0.4, mar=c(3.3,3.6,1.1,1.1))
}

savepdf6 <- function(file, width=16, height=8)
{
  fname <- paste(file,".pdf",sep="")
  pdf(fname, width=width/2.54, height=height/2.54,
      pointsize=10)
  par(mgp=c(2.2,0.45,0), tcl=-0.4, mar=c(3.3,3.6,1.1,1.1))
}
```

1. Compute effects for plots using the effects package
```{r}
e33 = effect("numlic", fit_multinom_v3)
e33 <- as.data.frame(e33)

e111 = effect("triplength_avg", fit_multinom_v3)
e111 = as.data.frame(e111)
e2222 = effect("income_numerical", fit_multinom_v3, xlevels = 20)
e2222 = as.data.frame(e2222)
e44 = effect("tripsavg", fit_multinom_v3)
e44 <- as.data.frame(e44)

e55 = effect("log(nummots1)", fit_multinom_v3)
e55 <- as.data.frame(e55)
e66 = effect("numped", fit_multinom_v3)
e66 <- as.data.frame(e66)

e100 =  effect("workers", fit_multinom_v3, xlevels=4)
e100 <- as.data.frame(e100)
e1111 =effect("parttime", fit_multinom_v3, xlevels =4)
e1111 <- as.data.frame(e1111)

e144 = effect("CSyes", fit_multinom_v3)
e144 <- as.data.frame(e144)
e155 = effect("CSmultiple", fit_multinom_v3)
e155 <- as.data.frame(e155)


e133 = effect("oldHH", fit_multinom_v3)
e133 <- as.data.frame(e133)
e244 = effect("hh_children", fit_multinom_v3)
e244 <- as.data.frame(e244)


e177 = effect("bus28", fit_multinom_v3)
e177 <- as.data.frame(e177)
e188 = effect("metro28", fit_multinom_v3)
e188 <- as.data.frame(e188)
e199 = effect("train28", fit_multinom_v3)
e199 <- as.data.frame(e199)

e200 = effect("housing_type",fit_multinom_v3)
e200 <- as.data.frame(e200)
e211 = effect("garage", fit_multinom_v3)
e211<- as.data.frame(e211)
e166 = effect("region2", fit_multinom_v3)
e166 <- as.data.frame(e166)

e222 = effect("quali_opnv", fit_multinom_v3)
e222 <- as.data.frame(e222)
e233 = effect("quali_nv", fit_multinom_v3)
e233 <- as.data.frame(e233)

```


2. Make effect plots with ggplot2

2.1 Number of licenses and monthly income
```{r}

numlic_plot <-ggplot(data=e33, aes(x=numlic))+
      geom_line(aes(y=prob.X0, color="Zero cars")) + 
      geom_line(aes(y=prob.X1, color="One car")) + 
      geom_line(aes(y=prob.X2, color ="Two cars"))+
      geom_line(aes(y=prob.X3, color ="Three or more cars"))+
      ylab("Predicted Probability")+
      xlab("Number of licensed drivers")+
      ggtitle("Licenses")+
      labs(color = "Number of cars owned:") +
      scale_color_manual(values = c("#e08f62", "#c70039", "#70af85","#111d5e"), breaks = c("Zero cars", "One car","Two cars", "Three or more cars"))+
      coord_fixed(ratio=4)+
      scale_y_continuous(limits=c(0,1),breaks = c(0.2,0.4,0.6,0.8))+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
              text=element_text(family="Times"),
              axis.title = element_text(size = 12),
              legend.title = element_text(size = 10),
        panel.grid.minor=element_blank())+
      scale_fill_grey()
```
2.2 Income
```{r}

income_plot <-ggplot(data=e2222, aes(x=income_numerical))+
      geom_line(aes(y=prob.X0, color="Zero cars")) + 
      geom_line(aes(y=prob.X1, color="One car")) + 
      geom_line(aes(y=prob.X2, color ="Two cars"))+
      geom_line(aes(y=prob.X3, color ="Three or more cars"))+
      ylab("Predicted Probability")+
      xlab("Monthly Income in Thousands")+
      ggtitle("Income")+
      labs(color = "Number of cars owned:") +
      coord_fixed(ratio=9)+
      scale_y_continuous(limits=c(0,1),breaks = c(0.2,0.4,0.6,0.8))+
      scale_color_manual(values = c("#e08f62", "#c70039", "#70af85","#111d5e"), breaks = c("Zero cars", "One car","Two cars", "Three or more cars"))+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
        legend.position = "bottom",
        text=element_text(family="Times"),
        axis.title = element_text(size = 12),
        legend.title = element_text(size = 10),
        plot.title = element_text(size = 12),
        panel.grid.minor=element_blank())+
      scale_fill_grey()
income_plot


figure_incnum <- ggarrange(numlic_plot, income_plot,common.legend = TRUE, legend = "right", vjust=6,hjust=-0.6, ncol = 2, nrow = 1, align="h")

savepdf("numlic")
annotate_figure(figure_incnum)
dev.off()

```
2.3 Carsharing

```{r}
CS1_plot <-ggplot(data=e144, aes(x=CSyes, group=1))+
      geom_line(aes(y=prob.X0, color="Zero cars")) + 
      geom_line(aes(y=prob.X1, color="One car")) + 
      geom_line(aes(y=prob.X2, color ="Two cars"))+
      geom_line(aes(y=prob.X3, color ="Three or more cars"))+
      ylab("Predicted Probability")+
      xlab("One carsharing subsciption")+
      ggtitle("Carsharing")+
      labs(color = "Number of cars owned:") +
      coord_fixed(ratio=2)+
      scale_y_continuous(limits=c(0,1),breaks = c(0.2,0.4,0.6,0.8))+
      scale_color_manual(values = c("#e08f62", "#c70039", "#70af85","#111d5e"), breaks = c("Zero cars", "One car","Two cars", "Three or more cars"))+
      scale_x_discrete(labels = c("0" = "No", "1" = "Yes"))+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
                text=element_text(family="Times"),
        axis.title = element_text(size = 12),
        legend.title = element_text(size = 10),
        plot.title = element_text(size = 12),
        panel.grid.minor=element_blank())+
      scale_fill_grey()


CS2_plot <-ggplot(data=e155, aes(x=CSmultiple, group=1))+
      geom_line(aes(y=prob.X0, color="Zero cars")) + 
      geom_line(aes(y=prob.X1, color="One car")) + 
      geom_line(aes(y=prob.X2, color ="Two cars"))+
      geom_line(aes(y=prob.X3, color ="Three or more cars"))+
      ylab("Predicted Probability")+
      xlab("Multiple carsharing subscriptions")+
      ggtitle("M.carsharing")+
      labs(color = "Number of cars owned:") +
     scale_color_manual(values = c("#e08f62", "#c70039", "#70af85","#111d5e"), breaks = c("Zero cars", "One car","Two cars", "Three or more cars"))+
      coord_fixed(ratio=2)+
      scale_y_continuous(limits=c(0,1),breaks = c(0.2,0.4,0.6,0.8))+
      scale_x_discrete(labels = c("0" = "No", "1" = "Yes"))+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
              text=element_text(family="Times"),
        axis.title = element_text(size = 12),
        legend.title = element_text(size = 10),
        plot.title = element_text(size = 12),
        legend.position = "bottom",
        panel.grid.minor=element_blank())+
      scale_fill_grey()

figure_CS <- ggarrange(CS1_plot,CS2_plot, common.legend = TRUE, legend = "right",
          ncol = 2, nrow = 1)

savepdf("CS")
annotate_figure(figure_CS)
dev.off()

```



2.4 Tripsavg and triplength_avg

```{r}


trips_plot <-ggplot(data=e44, aes(x=tripsavg))+
      geom_line(aes(y=prob.X0, color="Zero cars")) + 
      geom_line(aes(y=prob.X1, color="One car")) + 
      geom_line(aes(y=prob.X2, color ="Two cars"))+
      geom_line(aes(y=prob.X3, color ="Three or more cars"))+
      ylab("Predicted Probability")+
      xlab("Average number of trips")+
      ggtitle("Av. trips")+
      labs(color = "Number of cars owned:") +
      coord_fixed(ratio=8)+
      scale_y_continuous(limits=c(0,1),breaks = c(0.2,0.4,0.6,0.8))+
  scale_x_continuous(limits=c(0,8))+
  scale_color_manual(values = c("#e08f62", "#c70039", "#70af85","#111d5e"), breaks = c("Zero cars", "One car","Two cars", "Three or more cars"))+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
                   text=element_text(family="Times"),
        axis.title = element_text(size = 12),
        legend.title = element_text(size = 10),
        plot.title = element_text(size = 12),
        panel.grid.minor=element_blank())+
      scale_fill_grey()

triplength_plot <-ggplot(data=e111, aes(x=triplength_avg))+
      geom_line(aes(y=prob.X0, color="Zero cars")) + 
      geom_line(aes(y=prob.X1, color="One car")) + 
      geom_line(aes(y=prob.X2, color ="Two cars"))+
      geom_line(aes(y=prob.X3, color ="Three or more cars"))+
      ylab("Predicted Probability")+
      xlab("Average trip length in km")+
      ggtitle("Av. triplength")+
      labs(color = "Number of cars owned:") +
      coord_fixed(ratio=33)+
      scale_y_continuous(limits=c(0,1),breaks = c(0.2,0.4,0.6,0.8))+
      scale_x_continuous(limits=c(0,33))+
  scale_color_manual(values = c("#e08f62", "#c70039", "#70af85","#111d5e"), breaks = c("Zero cars", "One car","Two cars", "Three or more cars"))+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
                   text=element_text(family="Times"),
        axis.title = element_text(size = 12),
        legend.title = element_text(size = 10),
        plot.title = element_text(size = 12),
        legend.position = "bottom",
        plot.margin=unit(c(0,0,0,0),"pt"),
        panel.grid.minor=element_blank())+
      scale_fill_grey()



figure_trips <- ggarrange(triplength_plot,trips_plot, common.legend = TRUE, legend = "right", vjust=6, align = "v",
          ncol = 2, nrow = 1)

annotate_figure(figure_trips)

savepdf("trips")
annotate_figure(figure_trips)
dev.off()



```

2.5 Full-time and part-time workers

```{r}

workers_plot <-ggplot(data=e100, aes(x=workers))+
      geom_line(aes(y=prob.X0, color="Zero cars")) + 
      geom_line(aes(y=prob.X1, color="One car")) + 
      geom_line(aes(y=prob.X2, color ="Two cars"))+
      geom_line(aes(y=prob.X3, color ="Three or more cars"))+
      ylab("Predicted Probability")+
      xlab("Number of full-time workers")+
      ggtitle("Full-time")+
      labs(color = "Number of cars owned:") +
      coord_fixed(ratio=3)+
      scale_y_continuous(limits=c(0,1),breaks = c(0.2,0.4,0.6,0.8))+
        scale_color_manual(values = c("#e08f62", "#c70039", "#70af85","#111d5e"), breaks = c("Zero cars", "One car","Two cars", "Three or more cars"))+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
               text=element_text(family="Times"),
        axis.title = element_text(size = 12),
        legend.title = element_text(size = 10),
        plot.title = element_text(size = 12),
        legend.position = "bottom",
        panel.grid.minor=element_blank())+
      scale_fill_grey()
workers_plot

parttime_plot <-ggplot(data=e1111, aes(x=parttime))+
      geom_line(aes(y=prob.X0, color="Zero cars")) + 
      geom_line(aes(y=prob.X1, color="One car")) + 
      geom_line(aes(y=prob.X2, color ="Two cars"))+
      geom_line(aes(y=prob.X3, color ="Three or more cars"))+
      ylab("Predicted Probability")+
      xlab("Number of part-time workers")+
      ggtitle("Part-time")+
      labs(color = "Number of cars owned:") +
      coord_fixed(ratio=3)+
      scale_y_continuous(limits=c(0,1),breaks = c(0.2,0.4,0.6,0.8))+
        scale_color_manual(values = c("#e08f62", "#c70039", "#70af85","#111d5e"), breaks = c("Zero cars", "One car","Two cars", "Three or more cars"))+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
               text=element_text(family="Times"),
        axis.title = element_text(size = 12),
        legend.title = element_text(size = 10),
        plot.title = element_text(size = 12),
        legend.position = "bottom",
        panel.grid.minor=element_blank())+
      scale_fill_grey()



figure_workers <- ggarrange(workers_plot, parttime_plot,common.legend = TRUE, legend = "right",
          ncol = 2, nrow = 1)


annotate_figure(figure_workers)

savepdf("workers")
annotate_figure(figure_workers)
dev.off()
```

2.6 Households with children and households with older age compositions

```{r}

children_plot <-ggplot(data=e244, aes(x=hh_children, group = 1))+
      geom_line(aes(y=prob.X0, color="Zero cars")) + 
      geom_line(aes(y=prob.X1, color="One car")) + 
      geom_line(aes(y=prob.X2, color ="Two cars"))+
      geom_line(aes(y=prob.X3, color ="Three or more cars"))+
      ylab("Predicted Probability")+
      xlab("Household with children")+
      ggtitle("Children")+
      labs(color = "Number of cars owned:") +
      coord_fixed(ratio=2)+
      scale_y_continuous(limits=c(0,1),breaks = c(0.2,0.4,0.6,0.8))+
              scale_color_manual(values = c("#e08f62", "#c70039", "#70af85","#111d5e"), breaks = c("Zero cars", "One car","Two cars", "Three or more cars"))+
      scale_x_discrete(labels = c("0" = "No", "1" = "Yes"))+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),    
              text=element_text(family="Times"),
        axis.title = element_text(size = 12),
        legend.title = element_text(size = 10),
        plot.title = element_text(size = 12),
        #axis.text.x = element_text(angle=45, hjust=1),
        panel.grid.minor=element_blank())+
      scale_fill_grey()


old_plot <-ggplot(data=e133, aes(x=oldHH, group=1))+
      geom_line(aes(y=prob.X0, color="Zero cars")) + 
      geom_line(aes(y=prob.X1, color="One car")) + 
      geom_line(aes(y=prob.X2, color ="Two cars"))+
      geom_line(aes(y=prob.X3, color ="Three or more cars"))+
      ylab("Predicted Probability")+
      xlab("Prevailing household generation")+
      ggtitle("Generation")+
      labs(color = "Number of cars owned:") +
      coord_fixed(ratio=2)+
      scale_y_continuous(limits=c(0,1),breaks = c(0.2,0.4,0.6,0.8))+
              scale_color_manual(values = c("#e08f62", "#c70039", "#70af85","#111d5e"), breaks = c("Zero cars", "One car","Two cars", "Three or more cars"))+
      scale_x_discrete(limits=c("0","1"),labels = c("0" = "Gen. Y and Z", "1" = "Gen. X+"))+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
                  text=element_text(family="Times"),
        axis.title = element_text(size = 12),
        legend.title = element_text(size = 10),
        plot.title = element_text(size = 12),
             # axis.text.x = element_text(angle=45, hjust=1),
        panel.grid.minor=element_blank())+
      scale_fill_grey()
share2_plot


figure_chidold<- ggarrange(children_plot, old_plot,common.legend = TRUE, legend = "right", vjust=2,
          ncol = 2, nrow = 1, align = "h")



annotate_figure(figure_chidold)

savepdf("chid")
annotate_figure(figure_chidold)
dev.off()

```

2.7 Number of bikes and number of motorbikes


```{r}
numped_plot <-ggplot(data=e66, aes(x=numped))+
      geom_line(aes(y=prob.X0, color="Zero cars")) + 
      geom_line(aes(y=prob.X1, color="One car")) + 
      geom_line(aes(y=prob.X2, color ="Two cars"))+
      geom_line(aes(y=prob.X3, color ="Three or more cars"))+
      ylab("Predicted Probability")+
      xlab("Number of bikes / pedelecs")+
      ggtitle("Bikes")+
      labs(color = "Number of cars owned:") +
      coord_fixed(ratio=10)+
      scale_y_continuous(limits=c(0,1),breaks = c(0.2,0.4,0.6,0.8))+
      scale_x_continuous(limits=c(0,10), breaks = c(0,2,4,6,8,10))+
      scale_color_manual(values = c("#e08f62", "#c70039", "#70af85","#111d5e"), breaks = c("Zero cars", "One car","Two cars", "Three or more cars"))+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
              text=element_text(family="Times"),
        axis.title = element_text(size = 12),
        legend.title = element_text(size = 10),
        plot.title = element_text(size = 12),
        panel.grid.minor=element_blank())+
      scale_fill_grey()

nummots_plot <-ggplot(data=e55, aes(x=nummots1))+
      geom_line(aes(y=prob.X0, color="Zero cars")) + 
      geom_line(aes(y=prob.X1, color="One car")) + 
      geom_line(aes(y=prob.X2, color ="Two cars"))+
      geom_line(aes(y=prob.X3, color ="Three or more cars"))+
      ylab("Predicted Probability")+
      xlab("Number of motorbikes / mopeds")+
      ggtitle("Motorbikes")+
      labs(color = "Number of cars owned:") +
      coord_fixed(ratio=4)+
      scale_y_continuous(limits=c(0,1),breaks = c(0.2,0.4,0.6,0.8))+
       scale_color_manual(values = c("#e08f62", "#c70039", "#70af85","#111d5e"), breaks = c("Zero cars", "One car","Two cars", "Three or more cars"))+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
              text=element_text(family="Times"),
        axis.title = element_text(size = 12),
        legend.title = element_text(size = 10),
        plot.title = element_text(size = 12),
        panel.grid.minor=element_blank())+
      scale_fill_grey()


figure_pedmots<- ggarrange(numped_plot, nummots_plot,common.legend = TRUE, legend = "right", vjust=6,
          ncol = 2, nrow = 1)


annotate_figure(figure_pedmots)

savepdf("ped")
annotate_figure(figure_pedmots)
dev.off()
```


2.8 Distance to train, bus and metro stations
```{r}
train_plot <-ggplot(data=e199, aes(x=train28, group=1))+
      geom_line(aes(y=prob.X0, color="Zero cars")) + 
      geom_line(aes(y=prob.X1, color="One car")) + 
      geom_line(aes(y=prob.X2, color ="Two cars"))+
      geom_line(aes(y=prob.X3, color ="Three or more cars"))+
      ylab("")+
      xlab("")+
      ggtitle("Train")+
      labs(color = "Number of cars owned:") +
      coord_fixed(ratio=3)+
scale_color_manual(values = c("#e08f62", "#c70039", "#70af85","#111d5e"), breaks = c("Zero cars", "One car","Two cars", "Three or more cars"))+      scale_y_continuous(limits=c(0,1),breaks = c(0.2,0.4,0.6,0.8))+
       scale_x_discrete(labels = c("near" = "< 0.5 km", "middle"="0.5 - 2.5 km","far"="2.5 - 5 km", "rfar" = "> 5 km"))+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
              text=element_text(family="Times"),
        axis.title = element_text(size = 12),
        legend.title = element_text(size = 10),
        plot.title = element_text(size = 12),
        axis.text.x = element_text(angle=45, hjust=1), 
        panel.grid.minor=element_blank())+
      scale_fill_grey()

bus_plot <-ggplot(data=e177, aes(x=bus28, group=1))+
      geom_line(aes(y=prob.X0, color="Zero cars")) + 
      geom_line(aes(y=prob.X1, color="One car")) + 
      geom_line(aes(y=prob.X2, color ="Two cars"))+
      geom_line(aes(y=prob.X3, color ="Three or more cars"))+
      scale_color_manual(values = c("#e08f62", "#c70039", "#70af85","#111d5e"), breaks = c("Zero cars", "One car","Two cars", "Three or more cars"))+
      ylab("Predicted Probability")+
      xlab("")+
      ggtitle("Bus")+
      labs(color = "Number of cars owned:") +
      coord_fixed(ratio=3)+
      scale_y_continuous(limits=c(0,1),breaks = c(0.2,0.4,0.6,0.8))+
       scale_x_discrete(labels = c("near" = "< 0.5 km", "middle"="0.5 - 2.5 km","far"="2.5 - 5 km", "rfar" = "> 5 km"))+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
              text=element_text(family="Times"),
        axis.title = element_text(size = 12),
        legend.title = element_text(size = 10),
        plot.title = element_text(size = 12),
        axis.text.x = element_text(angle=45, hjust=1), 
        legend.position = "bottom",
        panel.grid.minor=element_blank())+
      scale_fill_grey()
bus_plot

metro_plot <-ggplot(data=e188, aes(x=metro28, group = 1))+
      geom_line(aes(y=prob.X0, color="Zero cars")) + 
      geom_line(aes(y=prob.X1, color="One car")) + 
      geom_line(aes(y=prob.X2, color ="Two cars"))+
      geom_line(aes(y=prob.X3, color ="Three or more cars"))+
      ylab("")+
      xlab("")+
      ggtitle("Metro")+
      labs(color = "Number of cars owned:") +
      coord_fixed(ratio=3)+
      scale_y_continuous(limits=c(0,1),breaks = c(0.2,0.4,0.6,0.8))+
   scale_color_manual(values = c("#e08f62", "#c70039", "#70af85","#111d5e"), breaks = c("Zero cars", "One car","Two cars", "Three or more cars"))+
      scale_x_discrete(labels = c("near" = "< 0.5 km", "middle"="0.5 - 2.5 km","far"="2.5 - 5 km", "rfar" = "> 5 km"))+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
              text=element_text(family="Times"),
        axis.title = element_text(size = 12),
        legend.title = element_text(size = 10),
        plot.title = element_text(size = 12),
        axis.text.x = element_text(angle=45, hjust=1),     
        panel.grid.minor=element_blank())+
      scale_fill_grey()


figure_bus<- ggarrange(bus_plot, metro_plot,train_plot,common.legend = TRUE, legend = c("none"), vjust=4,
          ncol = 3, nrow = 1) %>% gridExtra::grid.arrange(get_legend(bus_plot), heights = unit(c(60, 5), "mm"))


annotate_figure(figure_bus,
                left = text_grob("Predicted Probability", color = "black", rot = 90, family = "Times", size="12", hjust=0.2),
                bottom=text_grob("Distance to next station in km", color="black",vjust=-10,family = "Times", size="12")
)

savepdf4("bus")
annotate_figure(figure_bus,
                bottom=text_grob("Distance to next station in km", color="black",vjust=-3.5,family = "Times", size="12")
)
dev.off()
```


2.9 Housing type and the availability of a garage

```{r}

region_plot <-ggplot(data=e166, aes(x=region2, group=1))+
      geom_line(aes(y=prob.X0, color="Zero cars")) + 
      geom_line(aes(y=prob.X1, color="One car")) + 
      geom_line(aes(y=prob.X2, color ="Two cars"))+
      geom_line(aes(y=prob.X3, color ="Three or more cars"))+
      ylab("Predicted Probability")+
      xlab("Regional area")+
      ggtitle("Region")+
      labs(color = "Number of cars owned") +
      coord_fixed(ratio=2.25)+
      scale_y_continuous(limits=c(0,1),breaks = c(0.2,0.4,0.6,0.8))+
      scale_x_discrete(labels = c("urban" = "Urban", "suburban" = "Suburban","rural"= "Rural"))+
  scale_color_manual(values = c("#e08f62", "#c70039", "#70af85","#111d5e"), breaks = c("Zero cars", "One car","Two cars", "Three or more cars"))+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
        legend.position="bottom",
        text=element_text(family="Times"),
        axis.title = element_text(size = 12),
        legend.title = element_text(size = 12),
        plot.title = element_text(size = 12),
        axis.text.x = element_text(angle=45, hjust=1),
        panel.grid.minor=element_blank())+
      scale_fill_grey()


housing_plot <-ggplot(data=e200, aes(x=housing_type, group=1))+
      geom_line(aes(y=prob.X0, color="Zero cars")) + 
      geom_line(aes(y=prob.X1, color="One car")) + 
      geom_line(aes(y=prob.X2, color ="Two cars"))+
      geom_line(aes(y=prob.X3, color ="Three or more cars"))+
      ylab("Predicted Probability")+
      xlab("Type of housing")+
      ggtitle("Housing")+
      labs(color = "Number of cars owned") +
      coord_fixed(ratio=2.25)+
      scale_y_continuous(limits=c(0,1),breaks = c(0.2,0.4,0.6,0.8))+
   scale_color_manual(values = c("#e08f62", "#c70039", "#70af85","#111d5e"), breaks = c("Zero cars", "One car","Two cars", "Three or more cars"))+
      scale_x_discrete(limits = c("singlefamily_h", "multifamily_h", "apartmentbuilding"), labels = c("singlefamily_h" = "Single-family home", "multifamily_h" = "Multi-family home","apartmentbuilding" = "Apartment"))+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
              text=element_text(family="Times"),
        axis.title = element_text(size = 12),
        legend.title = element_text(size = 12),
        plot.title = element_text(size = 12),
        axis.text.x = element_text(angle=45,hjust=1),
        panel.grid.minor=element_blank())+
      scale_fill_grey()

garage_plot <-ggplot(data=e211, aes(x=garage, group=1))+
      geom_line(aes(y=prob.X0, color="Zero cars")) + 
      geom_line(aes(y=prob.X1, color="One car")) + 
      geom_line(aes(y=prob.X2, color ="Two cars"))+
      geom_line(aes(y=prob.X3, color ="Three or more cars"))+
      ylab("Predicted Probability")+
      xlab("Availability of a garage")+
      ggtitle("Garage")+
      labs(color = "Number of cars owned") +
      coord_fixed(ratio=1.5)+
      scale_y_continuous(limits=c(0,1),breaks = c(0.2,0.4,0.6,0.8))+
      scale_x_discrete(labels = c("0" = "No", "1" = "Yes"))+
  scale_color_manual(values = c("#e08f62", "#c70039", "#70af85","#111d5e"), breaks = c("Zero cars", "One car","Two cars", "Three or more cars"))+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
              text=element_text(family="Times"),
              legend.position = "bottom",
        axis.title = element_text(size = 12),
        legend.title = element_text(size = 12),
        plot.title = element_text(size = 12),
        axis.text.x = element_text(angle=45, hjust=1),
        panel.grid.minor=element_blank())+
      scale_fill_grey()


figure_housing<- ggarrange(housing_plot, garage_plot,region_plot, common.legend=TRUE,legend=c("none"),align="h",
          ncol = 3, nrow = 1)

annotate_figure(figure_housing)

savepdf4("housing")
annotate_figure(figure_housing)
dev.off()


```

2.10 Quality of public services and public transport

```{r}
qualinv_plot <-ggplot(data=e233, aes(x=quali_nv, group=1))+
      geom_line(aes(y=prob.X0, color="Zero cars")) + 
      geom_line(aes(y=prob.X1, color="One car")) + 
      geom_line(aes(y=prob.X2, color ="Two cars"))+
      geom_line(aes(y=prob.X3, color ="Three or more cars"))+
      ylab("Predicted Probability")+
      xlab("Quality of public services")+
      ggtitle("Public Services")+
      labs(color = "Number of cars owned:") +
      coord_fixed(ratio=4)+
      scale_y_continuous(limits=c(0,1),breaks = c(0.2,0.4,0.6,0.8))+
       scale_color_manual(values = c("#e08f62", "#c70039", "#70af85","#111d5e"), breaks = c("Zero cars", "One car","Two cars", "Three or more cars"))+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
              text=element_text(family="Times"),
        axis.title = element_text(size = 12),
        legend.title = element_text(size = 10),
        plot.title = element_text(size = 12),
        panel.grid.minor=element_blank())+
      scale_fill_grey()

qualiopnv_plot <-ggplot(data=e222, aes(x=quali_opnv, group=1))+
      geom_line(aes(y=prob.X0, color="Zero cars")) + 
      geom_line(aes(y=prob.X1, color="One car")) + 
      geom_line(aes(y=prob.X2, color ="Two cars"))+
      geom_line(aes(y=prob.X3, color ="Three or more cars"))+
      ylab("Predicted Probability")+
      xlab("Quality of public transport")+
      ggtitle("Public transport")+
      labs(color = "Number of cars owned:") +
      coord_fixed(ratio=4)+
      scale_y_continuous(limits=c(0,1),breaks = c(0.2,0.4,0.6,0.8))+
       scale_color_manual(values = c("#e08f62", "#c70039", "#70af85","#111d5e"), breaks = c("Zero cars", "One car","Two cars", "Three or more cars"))+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
              text=element_text(family="Times"),
        axis.title = element_text(size = 12),
        legend.title = element_text(size = 10),
        plot.title = element_text(size = 12),
        panel.grid.minor=element_blank())+
      scale_fill_grey()


figure_quali<- ggarrange(qualinv_plot, qualiopnv_plot,common.legend = TRUE, legend = "right", vjust=6,ncol = 2, nrow = 1)


annotate_figure(figure_quali)

savepdf("quality")
annotate_figure(figure_quali)
dev.off()
```








